---
title: "p8105_hw5_fir2103"
author: "Farizah Rob"
date: "2022-11-15"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(httr)
```


## Problem 1


## Problem 2

```{r}
homicide_data <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
names(homicide_data)
```

The raw data has `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns. The variable names are `r names(homicide_data)`. `uid` represents the ID variable, `victim_first` and `victim_last` are the first and last names of the victim. There are age and sex variables for the victim as well, alongisde city, state, latitude (`lat`) and (`long`). `disposition` states what whether the attacker was arrested or not and if the case is closed. 

```{r}
homicide_data <- 
  homicide_data %>%
  mutate(city_state = str_c(city, state, sep = ", "))

total_homicides <- homicide_data %>%
  group_by(city_state) %>%
  summarize(total_homicides = n()) 

unsolved_homicides <- homicide_data %>%
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>%
  group_by(city_state) %>%
  summarize(unsolved_homicides = n())

total_homicides %>%
  left_join(unsolved_homicides) %>%
  knitr::kable()
```






